Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-08-05 snapshot_system/eval1.tex
graph updates
update experiments

\begin{figure}[ht]
    \centering
    \begin{subfigure}%{.5\textwidth}
      \centering
      %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
            \begin{tikzpicture}
                %\pgfplotsset{every axis legend/.append style={font={\tiny}}}
                    \begin{axis}[
                    %font={\tiny},
                    tick label style={font=\scriptsize},
                    tick style=thin,
                    width=0.5\linewidth,
                    title={\small $p=100$},
                    cycle list={
                        {blue,thin,solid,mark=none},
                        {red,thin,densely dashed,mark=none},
                        {red,thin,densely dotted,mark=none}
                    },
                    xlabel={\tiny Failed nodes},
                    ylabel={\tiny VM Availability (\%)},
                    extra y ticks={99.9}, %if important numbers are missing
                    mark options=solid,
                    legend columns=-1,
                    legend style={
                        font=\small,
                        cells={anchor=west}, %legend entry alignment
                        legend pos=south west %legend position
                    },
                    legend to name=legend:vm-availability,
                    %reverse legend,
                    ]
                    \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
                    \addlegendentry{$VO\,6.3$ (optimistic)}
                    \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
                    \addlegendentry{$VC$ (expected)}
                    \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
                    \addlegendentry{$VC$ (worst-case)}
                    %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                    %\addlegendentry{$VO\,20$ (optimistic)}
                    \end{axis}
            \end{tikzpicture}
      %\caption{100 machine cluster.}
      \label{fig:vm-availability-100}
    \end{subfigure}%
    \begin{subfigure}%{.5\textwidth}
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
                    width=0.5\linewidth,
                    tick label style={font=\scriptsize},
                    tick style=thin,
		title={\small $p=100000$},
                cycle list={
                    {blue,thin,solid,mark=none},
                    {red,thin,densely dashed,mark=none},
                    {red,thin,densely dotted,mark=none}
                },
		xlabel={\tiny Failed nodes},
		ylabel={\tiny VM Availability (\%)},
		extra y ticks={99.99}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_100000.txt};
                %\addlegendentry{$VO\,6.3$ (optimistic)}
                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_100000.txt};
                %\addlegendentry{$VC\,1250$ (estimated)}
                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_100000.txt};
                %\addlegendentry{$VC\,2500000$ (worst-case)}
                %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                %\addlegendentry{$VO\,20$ (optimistic)}
		\end{axis}
	\end{tikzpicture}
        %\caption{100000 machine cluster.}
  \label{fig:vm-availability-100000}
\end{subfigure}
    \pgfplotslegendfromname{legend:vm-availability}
      \caption{Availability of VM backups for VO and VC models for
          varying degrees of block sharing. Non-PDS replication fixed
          at 3 and PDS replication increased to 4. VC worst-case
          is $V=25*p$, and expected-case is $\frac{V}{2}$
      \label{fig:vm-availability}

\end{figure}

@@

Figure\ref{fig:leakage} shows the average accumulated storage leakage resulted by daily
approximate deletions among all VMs. We see the storage leakage ratio is satisfactory: 
after 9 snapshot approximate deletions, there is only 1MB space leaked over every 10GB
of stored data. In addition, the leakage ratio grows linearly with the number of approximate deletions
as our analysis, which gives us a reliable prediction of when to trigger a accurate mark-and-sweep delete operation.

>>>>

\begin{figure}[htbp]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
                cycle multi list={
                    mline\nextlist
                    [2 of]mmark*\nextlist
                },
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
                \addlegendentry{$VC\,1250$ (estimated)}
                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
                \addlegendentry{$VC\,2500$ (worst-case)}
                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
                \addlegendentry{$VO\,6.3$ (optimistic)}
                %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                %\addlegendentry{$VO\,20$ (optimistic)}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for
  varying degrees of block sharing (i.e. average number of VMs that use a
  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
  Graph shown for 100 machine cluster.
  }
  \label{fig:vm-availability}
\end{figure}

@@

Figure \ref{fig:leakage} shows the average accumulated storage leakage resulted by daily
approximate deletions among all VMs. We see the storage leakage ratio is satisfactory: 
after 9 snapshot approximate deletions, there is only 1MB space leaked over every 10GB
of stored data. In addition, the leakage ratio grows linearly with the number of approximate deletions
as our analysis, which gives us a reliable prediction of when to trigger a accurate mark-and-sweep delete operation.
